\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{classic} 
\moderncvcolor{blue}    
\usepackage[scale=0.85, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage[utf8]{inputenc}

\name{Richemond Jagoum}{Tchioho}
\title{SRE | DevOps | Infrastructure Automation Engineer}
\address{Bangangté, Cameroon}{}{}
\phone[mobile]{+237 651 73 79 22}
\email{jagoum24@gmail.com}
\homepage{github.com/Jagoum}
\social[linkedin]{richemond-jagoum}

\begin{document}
\makecvtitle
\vspace{-1.5em}

\section{Summary}
\small{LPIC-1 \& LPIC-2 Certified Linux Administrator and DevOps Engineer with deep expertise in SRE principles and infrastructure-as-code. Specializing in high-availability Kubernetes orchestration, observability, and end-to-end automation. Proven track record of building resilient, self-healing systems from the ground up.}

\section{Core Expertise}
\cvitem{Infra \& Cloud}{Linux (LPI Certified), AWS, GCP, OpenStack, Kubernetes, Docker, VMware}
\cvitem{Automation}{Terraform, Ansible, Bash, Python, GitOps (ArgoCD), GitHub Actions, CI/CD}
\cvitem{SRE Tools}{Prometheus, Grafana, ELK Stack, Jaeger, Security Hardening}
\cvitem{Management}{Scrum Methodology, Mentorship, Team Leadership, Graphics Design}

\section{Professional Experience}
\cventry{2024--Pres.}{DevOps \& Linux Engineer (Trainee)}{adorsys}{Cameroon}{}{
\begin{itemize}
    \item Optimized CI/CD and managed multi-cloud infra (OpenStack/AWS/GCP).
    \item Implemented system-wide observability with Prometheus/Grafana/ELK.
    \item Hardened Linux server security and automated sysadmin tasks with Ansible.
\end{itemize}}

\cventry{2022--2023}{DevOps Engineer (Trainee)}{skyengpro}{Remote}{}{
\begin{itemize}
    \item Orchestrated K8s workloads and built automated Docker registry workflows.
    \item Developed Python/Bash tooling to reduce infrastructure provisioning time.
\end{itemize}}

\section{SRE \& Automation Projects}
\cvitem{Automation}{\textbf{Cloud Gauntlet}: A one-script solution deploying full K8s infra via Terraform, including Gitea, ArgoCD, and Keycloak for production-ready environments.}
\cvitem{Observability}{\textbf{SRE Lab}: Comprehensive HCL/Terraform repository for monitoring best practices.}
\cvitem{DevOps}{\textbf{Kubernetes Lab}: Practical lab for testing and learning K8s configurations.}

\section{Certifications \& Education}
\cvitem{LPI}{LPIC-1: Linux Administrator | LPIC-2: Linux Engineer}
\cvitem{Others}{Cisco Networking | Huawei HCIA-Storage (In Progress)}
\cvitem{Education}{GCE A/L (Highest Level) | Strong Technical \& Mathematical Background}

\section{Achievements}
\cvitem{Hackathons}{MIT Sloan Global AI Hackathon | Mountain Tech Hackathon}
\cvitem{Conferences}{BE GLOBAL Conference attendee | Focus on Infrastructure Resilience}

\end{document}
