\documentclass[11pt,a4paper,sans]{moderncv}

% Moderncv themes
\moderncvstyle{classic} % 'casual', 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}    % 'blue', 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% Character encoding
\usepackage[utf8]{inputenc}

% Personal data
\name{Richemond Jagoum}{Tchioho}
\title{DevOps Engineer | SRE | AI Engineering Enthusiast}
\address{Bangangté, Cameroon}{}{}
\phone[mobile]{+237 651 73 79 22} % Replace with actual if desired
\email{jagoum24@gmail.com}
\homepage{github.com/Jagoum}
\social[linkedin]{richemond-jagoum}

% Content
\begin{document}
\makecvtitle

\section{Summary}
Highly motivated DevOps/SRE Specialist and Linux Administrator (LPIC-1, LPIC-2 Certified) with a strong foundation in infrastructure automation, cloud-native architectures, and a growing expertise in AI Engineering. Passionate about building resilient, automated systems and exploring the intersection of DevOps and Artificial Intelligence through RAG systems and LLMs. Dedicated to continuous learning, with a deep interest in mathematical problem-solving and structured project management using Scrum.

\section{Experience}
\cventry{2024--Present}{DevOps Engineer \& Linux Admin (Pre-Employee/Trainee)}{adorsys}{Bangangté, Cameroon}{}{
\begin{itemize}
    \item Specialized in infrastructure automation and cloud platforms (OpenStack, AWS, GCP).
    \item Implemented CI/CD pipelines and infrastructure as code using Terraform and Ansible.
    \item Worked on monitoring and observability solutions (Prometheus, Grafana, ELK).
    \item Managed Linux server environments and ensured system security and stability.
\end{itemize}}

\cventry{2022--2023}{DevOps Engineer (Pre-Employee/Trainee)}{skyengpro}{Remote}{}{
\begin{itemize}
    \item Assisted in the orchestration of containerized applications using Kubernetes and Docker.
    \item Contributed to the development of automation scripts (Bash, Python) for routine tasks.
    \item Participated in the maintenance and optimization of cloud infrastructure.
\end{itemize}}

\section{Technical Skills}
\cvitem{Infrastructure}{Linux (LPIC Certified), OpenStack, AWS, GCP, Virtualization (VirtualBox, KVM)}
\cvitem{Automation}{Terraform, Ansible, Kubernetes, Docker, CI/CD, GitOps (ArgoCD)}
\cvitem{AI \& Data}{RAG Systems, LangChain, Qdrant, Neo4j, Python, Data Science (Learning)}
\cvitem{Languages}{Rust, Python, C/C++, TypeScript, Bash, SQL (PostgreSQL)}
\cvitem{Others}{Linux Security, Networking, Cisco, Huawei Storage (HCIA-Storage in progress)}

\section{Featured Projects}
\cvitem{Automation}{Cloud Gauntlet - End-to-end local K8s infrastructure automated via Terraform and a single entry script. Deploys Gitea (with runners), ArgoCD (GitOps), and Keycloak (Auth). Implemented a Todo app with automated CI/CD flows and manifest-based deployments.}
\cvitem{AI Search}{Semantic Search Engine - AI-driven search engine implementing semantic search capabilities (Python).}
\cvitem{AI Analysis}{AI VideoAds Analyser - Tool using AI/ML to analyze video advertisements (Python).}
\cvitem{DevOps}{Observability Lab - Infrastructure monitoring and SRE best practices implementation (HCL/Terraform).}
\cvitem{Cloud}{Kubernetes Lab - Practical repository for testing and learning Kubernetes configurations.}

\section{Certifications}
\cvitem{LPI}{LPIC-1: Linux Administrator, LPIC-2: Linux Engineer}
\cvitem{Networking}{Cisco Network Academy Courses}
\cvitem{Storage}{Huawei HCIA-Storage V5 (In Progress)}

\section{Soft Skills \& Achievements}
\cvitem{Leadership}{Mentorship, Team Leadership, and Graphics Design expert.}
\cvitem{Management}{Proficient in Scrum Methodology and Project Management.}
\cvitem{Interests}{Passionate about SRE, DevOps, Security, Mathematics, AI Engineering, and Data Science.}
\cvitem{Hackathons}{Participant in Global AI Hackathon (MIT Sloan Club), Mountain Tech Hackathon.}
\cvitem{Conferences}{BE GLOBAL Conference attendee.}

\section{Education}
\cvitem{GCE A/L}{Highest Level of Education (Cameroon)}
\cvitem{GCE O/L}{General Certificate of Education Ordinary Level}

\end{document}
