\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{classic} 
\moderncvcolor{blue}    
\usepackage[scale=0.85, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage[utf8]{inputenc}

\name{Richemond Jagoum}{Tchioho}
\title{Systems Programmer | Embedded C \& Rust Engineer}
\address{Bangangté, Cameroon}{}{}
\phone[mobile]{+237 651 73 79 22}
\email{jagoum24@gmail.com}
\homepage{github.com/Jagoum}
\social[linkedin]{richemond-jagoum}

\begin{document}
\makecvtitle
\vspace{-1.5em}

\section{Summary}
\small{Systems-level Engineer with a focus on high-performance development and embedded software. Proficient in Rust and C, with a strong background in Linux internals (LPIC Certified). Experienced in building robust backends, including web servers and e-commerce systems in Rust, and developing embedded software in C.}

\section{Technical Expertise}
\cvitem{Languages}{\textbf{Rust} (Safe/Concurrent systems), \textbf{C} (Embedded/Low-level), Python, Bash}
\cvitem{Systems}{Linux Internals, Kernels, LPIC-1/2 Certified, Networking, Embedded Systems}
\cvitem{Web/Backend}{Rust-based Web Servers, E-commerce Backends, API Design}
\cvitem{DevOps/CI}{Infrastructure as Code (Terraform), GitHub Actions, Docker, Unix Shell}

\section{Featured Development Projects}
\cvitem{Rust}{\textbf{E-commerce Backend}: High-performance commerce system built entirely in Rust, focusing on safety and concurrency.}
\cvitem{Rust}{\textbf{Custom Web Server}: Built a standalone web server from scratch in Rust to understand low-level network handling.}
\cvitem{Embedded}{\textbf{C Firmware}: Developed embedded software in C, optimizing for resource-constrained environments.}
\cvitem{Automation}{\textbf{Cloud Gauntlet}: Automated K8s infra using Terraform/Bash, showcasing systems-level automation skills.}

\section{Professional Experience}
\cventry{2024--Pres.}{Linux Engineer (Trainee)}{adorsys}{Cameroon}{}{
\begin{itemize}
    \item Managed Linux server environments, emphasizing security and system performance.
    \item Automated infrastructure orchestration using Ansible and shell scripting.
\end{itemize}}

\cventry{2022--2023}{Infrastructure Engineer (Trainee)}{skyengpro}{Remote}{}{
\begin{itemize}
    \item Containerized systems and optimized environments for low-latency applications.
\end{itemize}}

\section{Certifications \& Education}
\cvitem{LPI}{LPIC-1: Linux Administrator | LPIC-2: Linux Engineer}
\cvitem{Cisco}{Network Academy Courses - Strong understanding of network protocols.}
\cvitem{Education}{GCE A/L (Highest Level) | Advanced Mathematical Problem Solving}

\section{Achievements}
\cvitem{Hackathons}{MIT Sloan Global AI Hackathon Participant | Mountain Tech Hackathon}
\cvitem{Interests}{Embedded Systems, Rust ecosystem, Mathematical Modeling, Linux Security.}

\end{document}
