\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{classic} 
\moderncvcolor{blue}    
\usepackage[scale=0.85, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage[utf8]{inputenc}

\name{Richemond Jagoum}{Tchioho}
\title{AI Infrastructure Engineer | MLOps Specialist}
\address{Bangangté, Cameroon}{}{}
\phone[mobile]{+237 651 73 79 22}
\email{jagoum24@gmail.com}
\homepage{github.com/Jagoum}
\social[linkedin]{richemond-jagoum}

\begin{document}
\makecvtitle
\vspace{-1.5em}

\section{Summary}
\small{DevOps-focused Engineer bridging the gap between SRE and Artificial Intelligence. Specializing in RAG (Retrieval-Augmented Generation) systems, vector database orchestration, and large language model (LLM) infrastructure. Passionate about building intelligent, scalable software with a strong mathematical foundation.}

\section{AI \& Technical Skills}
\cvitem{AI Engineering}{RAG Systems, Vector DBs (Qdrant, Neo4j, Chroma), LangChain, LLM Ops}
\cvitem{Development}{Python (Data Science Libraries), Rust (High-performance backends), C, Bash}
\cvitem{ML Infrastructure}{Kubernetes, Docker, GPU Orchestration (Learning), GitHub Actions CI/CD}
\cvitem{Systems}{Linux Administrator (LPIC Certified), Infrastructure as Code (Terraform)}

\section{AI \& Data Projects}
\cvitem{Semantic Search}{\textbf{Semantic Engine}: AI-driven search engine implementing semantic vector similarity using Python and Vector DBs.}
\cvitem{Video AI}{\textbf{AI VideoAds Analyser}: Tool using AI/ML to analyze and categorize video advertisements efficiently.}
\cvitem{Infrastructure}{\textbf{Cloud Gauntlet}: Automated K8s environment (Terraform) serving as a robust base for deploying and scaling AI/ML applications.}

\section{Experience (DevOps for AI)}
\cventry{2024--Pres.}{DevOps Engineer (Trainee)}{adorsys}{Cameroon}{}{
\begin{itemize}
    \item Managed cloud-native infrastructure and CI/CD, providing the platform for scalable services.
    \item Implemented observability stacks crucial for tracking ML model performance and latentcies.
\end{itemize}}

\cventry{2022--2023}{Infrastructure Engineer (Trainee)}{skyengpro}{Remote}{}{
\begin{itemize}
    \item Orchestrated containerized workloads, optimizing environments for data-intensive apps.
\end{itemize}}

\section{Certifications \& Education}
\cvitem{LPI}{LPIC-1: Linux Administrator | LPIC-2: Linux Engineer}
\cvitem{Education}{GCE A/L (Highest Level) | Extensive self-learning in Data Science \& AI}
\cvitem{Mathematics}{Strong mathematical problem-solving skills applied to AI Engineering.}

\section{Achievements}
\cvitem{Hackathons}{Participant in MIT Sloan Global AI Hackathon | Mountain Tech Hackathon}
\cvitem{Community}{BE GLOBAL Conference attendee | Active learner in AI research and systems.}

\end{document}
